Drought-sensitive trees survive on deep water access in a tropical forest community

### 2020-08-05 manuscript.rmd
added error for ERD as 1SE

\begin{equation}
Growth_{t} = \frac{1}{n_{t}}\sum_{day=1}^{n_{t}} StdK_{leaf,~n} StdVPD_{n} + error
(\#eq:M2)
\end{equation}

@@

```{r erd-iso, eval = TRUE, echo = FALSE, message = FALSE, fig.align = 'center', out.width = "80%", fig.pos = 'H', results = "asis", fig.cap = paste0("\\label{lab-erd-iso}Modelled Effective Rooting Depth (ERD; mean $\\pm$ add error; m) versus dry season stable isotopic concentration $\\delta^2H$ (mean $\\pm$ 1SE; ‰) for ", length(unique(erd.iso$sp))," canopy species from Barro Colorado Island. Data from [@Meinzer:1999]. See Table  \\@ref(tab:spcodes) for scientific names corresponding to species codes.")}
knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/psi.corr_best.depth_xylem_sap_deltaD_phenology_Meinzer_gr.Psi.VPD.jpeg"))
```

@@

```{r sp-erd, eval = TRUE, echo = FALSE, message = FALSE, fig.align ='center', out.width = "60%", fig.pos = 'H', results = "asis", fig.cap= paste0("\\label{lab-sp-erd}Modelled Effective Rooting Depth (ERD; mean $\\pm$ (add error) in m) for ", length(erd.sp)," large, canopy species of Barro Colorado Island. See Table  \\@ref(tab:spcodes) for scientific names corresponding to species codes.")}
knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/ERD_by_sp_large_canopy.jpeg"))
```

```{r erd-hyd, eval = TRUE, echo = FALSE, message = FALSE, fig.align ='center', out.width = "60%", fig.pos = 'H', results = "asis", fig.cap = paste0("\\label{lab-erd-hyd}Modelled Effective Rooting Depth (ERD; mean $\\pm$ (add error) in m) versus hydraulic properties for eight large, canopy species found on Barro Colorado Island (Panama). *R*^2^ and *P*-values are given in panel insets.[X-Axis labels to be added: $K_{max}$ units as in Fig. 2. Water Potentials are in MPa.]")}
knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/Select_traits_depth.jpeg"))
```

@@

```{r erd-mort, eval = TRUE, echo = FALSE, message = FALSE, fig.align ='center', out.width = "40%", fig.pos = 'H', results = "asis", fig.cap = paste0("\\label{lab-erd-mort}Mortality rate (mean $\\pm$ 1SE) versus Modelled Effective Rooting Depth (ERD; mean $\\pm$ (add error) in m) for ", length(erd.mrate.sp)," canopy species found on Barro Colorado Island. *R*^2^ and *P*-values are given in panel insets.")}
knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/mortality_rate_by rdi.gr.jpeg"))
```

```{r erd-time, eval = TRUE, echo = FALSE, message = FALSE, fig.align ='center', out.width = "40%", fig.pos = 'H', results = "asis", fig.cap = paste0("\\label{lab-erd-time} Modelled Species Effective Rooting Depth (ERD; mean $\\pm$ (add error) in m) versus time spent below critical hydraulic threhold--the number of days for which $\\Psi_{soil,~z}$ was below $\\Psi_{crit}$, defined as $\\Psi_{80,~leaf}$, over 1990-2015, where z is the soil depth matching species ERD--for ", length(erd.mrate.sp), " canopy species found on Barro Colorado Island. Each circle represents a species. Circles are colored and jittered vertically around the named depths (ticks) for clarity. (Are *R*^2^ and *P*-values needed here?)")}
knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/mean_mfac vs. rdi.gr.jpeg"))
```

@@

```{r erd-growth, eval = TRUE, echo = FALSE, message = FALSE, fig.align ='center', out.width = "40%", fig.pos = 'H', results = "asis", fig.cap = "\\label{lab-erd-growth}Scatterplot between Effective Rooting Deoth (ERD) and mean growth rate $\\pm$ (add error) for xx large, canopy species."}
knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/adult_Growth_vs_udi_with_outliers_sp.jpeg"))
```

>>>>

\begin{equation}
Growth_{t} = \frac{1}{n_{t}}\sum_{day=1}^{n_{t}} StdK_{leaf,~z,~n} StdVPD_{n} + error
(\#eq:M2)
\end{equation}

@@

```{r erd-iso, eval = TRUE, echo = FALSE, message = FALSE, fig.align = 'center', out.width = "80%", fig.pos = 'H', results = "asis", fig.cap = paste0("\\label{lab-erd-iso}Modelled Effective Rooting Depth (ERD; mean $\\pm$ 1SE; m) versus dry season stable isotopic concentration $\\delta^2H$ (mean $\\pm$ 1SE; ‰) for ", length(unique(erd.iso$sp))," canopy species from Barro Colorado Island. Data from [@Meinzer:1999]. See Table  \\@ref(tab:spcodes) for scientific names corresponding to species codes.")}
knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/psi.corr_best.depth_xylem_sap_deltaD_phenology_Meinzer_gr.Psi.VPD.jpeg"))
```

@@

```{r sp-erd, eval = TRUE, echo = FALSE, message = FALSE, fig.align ='center', out.width = "60%", fig.pos = 'H', results = "asis", fig.cap= paste0("\\label{lab-sp-erd}Modelled Effective Rooting Depth (ERD; mean $\\pm$ 1SE in m) for ", length(erd.sp)," large, canopy species of Barro Colorado Island. See Table  \\@ref(tab:spcodes) for scientific names corresponding to species codes.")}
knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/ERD_by_sp_large_canopy.jpeg"))
```

```{r erd-hyd, eval = TRUE, echo = FALSE, message = FALSE, fig.align ='center', out.width = "60%", fig.pos = 'H', results = "asis", fig.cap = paste0("\\label{lab-erd-hyd}Modelled Effective Rooting Depth (ERD; mean $\\pm$ 1SE in m) versus hydraulic properties for eight large, canopy species found on Barro Colorado Island (Panama). *R*^2^ and *P*-values are given in panel insets.[X-Axis labels to be added: $K_{max}$ units as in Fig. 2. Water Potentials are in MPa.]")}
knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/Select_traits_depth.jpeg"))
```

@@

```{r erd-mort, eval = TRUE, echo = FALSE, message = FALSE, fig.align ='center', out.width = "40%", fig.pos = 'H', results = "asis", fig.cap = paste0("\\label{lab-erd-mort}Mortality rate (mean $\\pm$ 1SE) versus Modelled Effective Rooting Depth (ERD; mean $\\pm$ 1SE in m) for ", length(erd.mrate.sp)," canopy species found on Barro Colorado Island. *R*^2^ and *P*-values are given in panel insets.")}
knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/mortality_rate_by rdi.gr.jpeg"))
```

```{r erd-time, eval = TRUE, echo = FALSE, message = FALSE, fig.align ='center', out.width = "40%", fig.pos = 'H', results = "asis", fig.cap = paste0("\\label{lab-erd-time} Modelled Species Effective Rooting Depth (ERD; mean $\\pm$ 1SE in m) versus time spent below critical hydraulic threhold--the number of days for which $\\Psi_{soil,~z}$ was below $\\Psi_{crit}$, defined as $\\Psi_{80,~leaf}$, over 1990-2015, where z is the soil depth matching species ERD--for ", length(erd.mrate.sp), " canopy species found on Barro Colorado Island. Each circle represents a species. Circles are colored and jittered vertically around the named depths (ticks) for clarity. (Are *R*^2^ and *P*-values needed here?)")}
knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/mean_mfac vs. rdi.gr.jpeg"))
```

@@

```{r erd-growth, eval = TRUE, echo = FALSE, message = FALSE, fig.align ='center', out.width = "40%", fig.pos = 'H', results = "asis", fig.cap = "\\label{lab-erd-growth}Scatterplot between Effective Rooting Deoth (ERD) and mean growth rate $\\pm$ 1SE for xx large, canopy species."}
knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/adult_Growth_vs_udi_with_outliers_sp.jpeg"))
```
